Seg_sites_rarefaction

### 2024-09-30 scripts/seg_sites_rarefaction.Rmd
pre-resubmission commit

# Define parameters
```{r}
# define parameters
seed <- 231266
threads <- 25
allele_frequencies <- seq(.001, .1, by = .001) # allele frequencies
n1 <- 5000 # p1 gene copy number
n2 <- 500 # p2 gene copy number
k <- seq(10, 100, by = 10) # numbers to rarefact to
mcmcs <- seq(1000, 10000, by = 1000) # number of mcmc draws
max_missing <- 30 # maximum percentage of missing data in a locus, from a uniform dist

@@

f2 <- ggplot(F2data_densities, aes(x = x, y = y)) +
  geom_line() +
  geom_ribbon(aes(ymin = 0, ymax = y, fill = quant), show.legend = FALSE) +
  geom_vline(data = F2data_sums, aes(xintercept = nseg), color = colors[1]) +
  geom_vline(data = F2data_pi, aes(xintercept = lower), linetype = "dashed", color = colors[2]) +
  geom_vline(data = F2data_pi, aes(xintercept = upper), linetype = "dashed", color = colors[2]) +
  facet_grid(K~pop, labeller = label_parsed) +
  theme_bw() +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values = c("#004488", "#ffffff", "#004488")) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank()) +
  xlab(bquote(italic(N[S]))) +
  ylab("Density")

@@

f4a <- ggplot(ns_all[iters == 10000,], aes(x = K, y = nseg)) +
  geom_errorbar(data = unique(ns_all[iters == 10000, c("pop", "K", "iters", "i", "lower", "upper")]),
            aes(x = K + 3.7, ymin = lower, ymax = upper), color = "#DDAA33", size = 1,
            inherit.aes = FALSE, width = 2) +
  geom_point(data = unique(ns_all[iters == 10000, c("pop", "K", "iters", "i", "lower", "upper", "ENs")]),
             aes(x = K + 3.7, y = ENs), color = "#DDAA33", size = 7, shape = 45,
            inherit.aes = FALSE) +
  stat_ydensity(aes(group = K), draw_quantiles = c(.025, .5, .975), scale = "width", bw = .4,
                fill = NA, width = 6) +
  facet_wrap(~pop) +
  scale_y_continuous(breaks = seq(40, 100, by = 10), limits = c(40, 100)) +
  theme_bw() + 
  scale_x_continuous(breaks = k) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(N[S]))) +
  xlab(bquote(gamma))

f4b <- ggplot(ns_all[K == 50,], aes(x = iters, y = nseg)) +
  geom_errorbar(data = unique(ns_all[K == 50,c("pop", "K", "iters", "i", "lower", "upper")]),
            aes(x = iters + 370, ymin = lower, ymax = upper), color = "#DDAA33", size = 1,
            inherit.aes = FALSE, width = 200) +
  geom_point(data = unique(ns_all[K == 50, c("pop", "K", "iters", "i", "lower", "upper", "ENs")]),
             aes(x = iters + 370, y = ENs), color = "#DDAA33", size = 7, shape = 45,
            inherit.aes = FALSE) +
  stat_ydensity(aes(group = iters), draw_quantiles = c(.025, .5, .975), scale = "width", bw = .4,
                fill = NA, width = 600) +
  facet_wrap(~pop) +
  theme_bw() + 
  scale_y_continuous(breaks = seq(40, 100, by = 5), limits = c(80, 100)) +
  scale_x_continuous(breaks = mcmcs) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        axis.text.x = element_text(size = t.sizes[2], angle = 90, vjust = .5),
        strip.text = element_blank(),
        strip.background = element_blank(),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(N[S]))) +
  xlab("Number of Simulated Draws")

@@

ns_all_agg <- rbind(ns_all_agg, ns_all_agg_med)
FS2 <- ggplot(ns_all_agg, aes(x = K, y = ENs - nseg, color = pop)) +
  geom_point() +
  facet_grid(stat~iters) +
  khroma::scale_color_highcontrast() +
  geom_hline(yintercept = 0) +
  theme_bw() +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        axis.text.x = element_text(size = t.sizes[2], angle = 90, vjust = .5),
        strip.background = element_blank(),
        strip.text = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(E(N[S])) * " - " * italic(N[S,observed]))) +
  xlab(bquote(gamma)) +
  guides(color = guide_legend(title = "Population"))

@@

FS3 <- ggplot(mon_rare_res, aes(x = pop, y = Ns)) +
  geom_boxplot() +
  geom_point(alpha = .2, position = position_jitter(height = 0, width = .2)) +
  geom_point(data = seg_res_mon$weighted.means, aes(x = subfacet, y = seg_sites), color = "red", size = 4) +
  theme_bw() +
  ylab(bquote(italic(N[s]))) +
  xlab("Population") +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]))

>>>>

# Define parameters
```{r}
# define parameters
seed <- 231266
threads <- 25
allele_frequencies <- seq(.001, .5, by = .001) # allele frequencies
n1 <- 5000 # p1 gene copy number
n2 <- 500 # p2 gene copy number
k <- seq(10, 100, by = 10) # numbers to rarefact to
mcmcs <- seq(1000, 10000, by = 1000) # number of mcmc draws
max_missing <- 30 # maximum percentage of missing data in a locus, from a uniform dist

@@

f2 <- ggplot(F2data_densities, aes(x = x, y = y)) +
  geom_line() +
  geom_ribbon(aes(ymin = 0, ymax = y, fill = quant), show.legend = FALSE) +
  geom_vline(data = F2data_sums, aes(xintercept = nseg), color = colors[1]) +
  geom_vline(data = F2data_pi, aes(xintercept = lower), linetype = "dashed", color = colors[2]) +
  geom_vline(data = F2data_pi, aes(xintercept = upper), linetype = "dashed", color = colors[2]) +
  facet_grid(K~pop, labeller = label_parsed) +
  theme_bw() +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values = c("#004488", "#ffffff", "#004488")) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank()) +
  xlab(bquote(italic(S))) +
  ylab("Density")

@@

f4a <- ggplot(ns_all[iters == 10000,], aes(x = K, y = nseg)) +
  geom_errorbar(data = unique(ns_all[iters == 10000, c("pop", "K", "iters", "i", "lower", "upper")]),
            aes(x = K + 3.7, ymin = lower, ymax = upper), color = "#DDAA33", size = 1,
            inherit.aes = FALSE, width = 2) +
  geom_point(data = unique(ns_all[iters == 10000, c("pop", "K", "iters", "i", "lower", "upper", "ENs")]),
             aes(x = K + 3.7, y = ENs), color = "#DDAA33", size = 7, shape = 45,
            inherit.aes = FALSE) +
  stat_ydensity(aes(group = K), draw_quantiles = c(.025, .5, .975), scale = "width", bw = .4,
                fill = NA, width = 6) +
  facet_wrap(~pop) +
  scale_y_continuous(breaks = seq(430, 500, by = 10), limits = c(430, 500)) +
  theme_bw() + 
  scale_x_continuous(breaks = k) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        strip.text = element_text(size = t.sizes[1]),
        strip.background = element_blank(),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(S))) +
  xlab(bquote(gamma))

f4b <- ggplot(ns_all[K == 50,], aes(x = iters, y = nseg)) +
  geom_errorbar(data = unique(ns_all[K == 50,c("pop", "K", "iters", "i", "lower", "upper")]),
            aes(x = iters + 370, ymin = lower, ymax = upper), color = "#DDAA33", size = 1,
            inherit.aes = FALSE, width = 200) +
  geom_point(data = unique(ns_all[K == 50, c("pop", "K", "iters", "i", "lower", "upper", "ENs")]),
             aes(x = iters + 370, y = ENs), color = "#DDAA33", size = 7, shape = 45,
            inherit.aes = FALSE) +
  stat_ydensity(aes(group = iters), draw_quantiles = c(.025, .5, .975), scale = "width", bw = .4,
                fill = NA, width = 600) +
  facet_wrap(~pop) +
  theme_bw() + 
  scale_y_continuous(breaks = seq(480, 500, by = 5), limits = c(480, 500)) +
  scale_x_continuous(breaks = mcmcs) +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        axis.text.x = element_text(size = t.sizes[2], angle = 90, vjust = .5),
        strip.text = element_blank(),
        strip.background = element_blank(),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(S))) +
  xlab("Number of Simulated Draws")

@@

ns_all_agg <- rbind(ns_all_agg, ns_all_agg_med)
FS2 <- ggplot(ns_all_agg, aes(x = K, y = ENs - nseg, color = pop)) +
  geom_point() +
  facet_grid(stat~iters) +
  khroma::scale_color_highcontrast() +
  geom_hline(yintercept = 0) +
  theme_bw() +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]),
        axis.text.x = element_text(size = t.sizes[2], angle = 90, vjust = .5),
        strip.background = element_blank(),
        strip.text = element_text(size = t.sizes[1]),
        legend.text = element_text(size = t.sizes[2])) +
  ylab(bquote(italic(S^"'") * " - " * italic(S))) +
  xlab(bquote(gamma)) +
  guides(color = guide_legend(title = "Population"))

@@

FS3 <- ggplot(mon_rare_res, aes(x = pop, y = Ns)) +
  geom_boxplot() +
  geom_point(alpha = .2, position = position_jitter(height = 0, width = .2)) +
  geom_point(data = seg_res_mon$weighted.means, aes(x = subfacet, y = seg_sites), color = "red", size = 4) +
  theme_bw() +
  ylab(bquote(italic(S))) +
  xlab("Population") +
  theme(axis.text = element_text(size = t.sizes[2]),
        axis.title = element_text(size = t.sizes[1]),
        legend.title = element_text(size = t.sizes[1]))
